2.6: Inferential Statistics I

### 2019-10-03 static/slides/12-slides.Rmd
Tweak slides 12 more

- Fortunately, some statisticians realized ["**there is only one test**"](https://allendowney.blogspot.com/2011/05/there-is-only-one-test.html) and some clever folks built a nice `R` package called `infer`

1. Calculate a statistic, $\delta$<sup>1</sup>, from a sample of data

2. Simulate a world where $\delta$ is null

3. Examine $\delta$ in the null world

4. Calculate the probability that $\delta$ could exist in the null world

5. Decide if $\delta$ is statistically significant

@@

- `infer` allows you to run through these steps manually to understand the process

@@

4. `calculate()`

@@

5. `visualize()`

@@

# Hypothesis Testing with the infer Package III

>>>>

- Fortunately, some clever statisticians realized ["**there is only one test**"](https://allendowney.blogspot.com/2011/05/there-is-only-one-test.html) and built a nice `R` package called `infer`

1. **Calculate** a statistic, $\delta_i$<sup>1</sup>, from a sample of data

2. **Simulate** a world where $\delta$ is null $(H_0)$

3. **Examine** the distribution of $\delta$ across the null world

4. **Calculate** the probability that $\delta_i$ could exist in the null world

5. **Decide** if $\delta_i$ is statistically significant

@@

- `infer` allows you to run through these steps manually to understand the process:

@@

4. `calculate()` the $p$-value

@@

5. `visualize()` with a histogram (optional)

@@
